### 2016-03-22 paper.tex
Add context section

>>>>

\section{Context}

Investigating the potential for player-narration games to teach
cultural empathy brought our team into a partnership with
\textit{a local library branch hidden for blind review}. This branch
serves primarily patrons from low socio-economic status, although
its special technology education programs also draw homeschoolers from
around the region.
The youth patrons of the library tend to be 4rd--6th grade 
``latchkey kids'' who 
see the library as a place to visit with friends, to participate in programs,
and to access technology.

Conversations with program coordinators about player-narration games
revealed that despite other differences, the youth patrons shared
a fascination with monsters, horror, and the macabre. 
This is in part because of cultural taboo: the youth will brag about
being able to see a PG-13-rated movie or play an M-rated game,
for example, and several kids worked together to produce an original
short movie based on battles between movie monsters.

The fascination exhibited by the youth patrons reflects various theses
of Cohen's monster theory~\citep{Cohen1996}. 
We see in their behavior that ``the same creatures who terrify and
interdict can evoke potent escapist fantasies''~(p.16).
Recognizing the youth patrons' attraction to this theme,
Cohen's theory establishing monsters as reflections of culture,
and the narrative potential of monsters,
our team decided to engage in a design experiment to validate our
hypotheses about player-narration games,
in collaboration with \textit{the library branch}.
